Interval Probability for Fuzzy Quantum Theories

### 2016-06-16 prob.tex
prob.tex modifying texts...

If the field of strength does not perfectly direct to the $z$-axis,
we does not really test the quantum event we want to test. This problem
will be handled later when we introduce the discrete quantum theory.
Even if the field of strength is perfectly direct to the $z$-axis,
the variant velocity makes spots broader and more washed out. Together
with the precision limit of the detector, it may sometimes be hard
to decide a particle corresponding to which state\footnote{\yutsung{Add citations to support the idea... Haven't find suitable
ones...}}. Similar to Buffon's needles, this kind of fuzziness can be taken
into account by associating each quantum event with an interval-valued
probability~$\left[l,r\right]$.

@@

As mentioned above, each quantum event~$P$ will be associated with
an interval-valued probability~$\left[l,r\right]$. Notice that whenever
the magnetic field of the Stern-Gerlach is fixed, i.e., an ideal measurement
is picked, measuring the spin is up or down is exactly the same as
tossing a coin. In another word, if somebody claimed she is tossing
a coin behind a veil, and only show the resulting heads or tails,
we cannot distinguish whether she has really tossed a coin, or she
has run an Stern-Gerlach experiment, and show us the head, the tail,
or the side of coin if the silver atoms is spin up, spin down, or
just hit the middle. Therefore, applying interval-valued

@@

\yutsung{About continuity, one of the confusion comes from the subtle
correspondence between the measurement processes and observables.
Consider the following observables and their measurement processes:
\begin{itemize}
\item The observable operator~$\mathbf{O}_{x}=\proj{1}+x\proj{-1}$. Except
$x=1$, the measurement process for $\mathbf{O}_{x}$ is ${\cal O}_{x}$:
\begin{enumerate}
\item With probability~$\mu_{\phi}\left(\proj{1}\right)$, return the measurement
result~$1$ with the post-measurement state~$\ket{1}$;
\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
result~$0$ with the post-measurement state~$\ket{0}$;
\item With probability~$\mu_{\phi}\left(\proj{-1}\right)$, return the
measurement result~$x$ with the post-measurement state~$\ket{-1}$.
\end{enumerate}
\item The observable operator~$\mathbf{J}_{z}^{2}=\proj{1}+\proj{-1}$,
and its measurement process~${\cal J}_{z}^{2}$:
\begin{enumerate}
\item With probability~$\mu_{\phi}\left(\proj{1}+\proj{-1}\right)$, return
the measurement result~$1$ with the post-measurement state~$\ket{1}\ip{1}{\phi}+\ket{-1}\ip{-1}{\phi}$;
\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
result~$0$ with the post-measurement state~$\ket{0}$.
\end{enumerate}
\end{itemize}
As an operator, it is clear that $\lim_{x\rightarrow1}\mathbf{O}_{x}=\mathbf{J}_{z}^{2}$,
and we should have $\lim_{x\rightarrow1}{\cal O}_{x}={\cal O}_{1}$
for the measurement process. However, it is not obvious why ${\cal O}_{1}={\cal J}_{z}^{2}$.
Although they have the same probability for the measurement results,
but their post-measurement states are different. This might be a defect
of representing a measurement process as an observable. As $\mathbf{O}_{1}=\mathbf{J}_{z}^{2}$,
there is no observable corresponding to the measurement process~${\cal O}_{1}$.}

>>>>

If the field of strength does not perfectly direct to the $z$-axis,
we does not really test the quantum event we want to test. This problem
will be handled later when we introduce the discrete quantum theory.
Even if the field of strength is perfectly direct to the $z$-axis,
the variant velocity makes spots broader and more washed out. Together
with the precision limit of the detector, it may sometimes be hard
to decide a particle corresponding to which state\footnote{\yutsung{Add citations to support the idea... Haven't found suitable
ones...}}. Similar to Buffon's needles, this kind of fuzziness can be taken
into account by associating each quantum event with an interval-valued
probability~$\left[l,r\right]$.

@@

As mentioned above, each quantum event~$P$ will be associated with
an interval-valued probability~$\left[l,r\right]$. Notice that whenever
the magnetic field of the Stern-Gerlach is fixed, i.e., an ideal measurement
is picked, measuring the spin is exactly the same as tossing a coin.
In another word, if somebody claimed she is tossing a coin behind
a veil, and only show the resulting heads or tails, we cannot distinguish
whether she has really tossed a coin, or she has run an Stern-Gerlach
experiment, and show us the head, the tail, or the side of coin if
the silver atoms is spin up, spin down, or just hit the middle, respectively.
Therefore, we should plug in the definition of interval-valued probability
measure into the definition of quantum probability space for each
ideal measurement, and get the following definition.

@@

\yutsung{About continuity, one of the confusion comes from the subtle
correspondence between the measurement processes and observables.
Consider the following observables and their measurement processes:
\begin{itemize}
\item For any $x\in\R$, consider the observable operator~$\mathbf{O}_{x}=\proj{1}+x\proj{-1}$.
Except $x=1$, given the system in the state~$\ket{\phi}$, we can
denote the measurement process for $\mathbf{O}_{x}$ by ${\cal O}_{x}$:
\begin{enumerate}
\item With probability~$\mu_{\phi}\left(\proj{1}\right)$, return the measurement
result~$1$ with the post-measurement state~$\ket{1}$;
\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
result~$0$ with the post-measurement state~$\ket{0}$;
\item With probability~$\mu_{\phi}\left(\proj{-1}\right)$, return the
measurement result~$x$ with the post-measurement state~$\ket{-1}$.
\end{enumerate}
\item The observable operator~$\mathbf{J}_{z}^{2}=\proj{1}+\proj{-1}$,
and its measurement process~${\cal J}_{z}^{2}$:
\begin{enumerate}
\item With probability~$\mu_{\phi}\left(\proj{1}+\proj{-1}\right)$, return
the measurement result~$1$ with the post-measurement state~$\ket{1}\ip{1}{\phi}+\ket{-1}\ip{-1}{\phi}$;
\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
result~$0$ with the post-measurement state~$\ket{0}$.
\end{enumerate}
\end{itemize}
As an operator, it is clear that $\lim_{x\rightarrow1}\mathbf{O}_{x}=\mathbf{J}_{z}^{2}$,
and we should have $\lim_{x\rightarrow1}{\cal O}_{x}={\cal O}_{1}$
for the measurement process. However, it is not obvious why ${\cal O}_{1}={\cal J}_{z}^{2}$.
Although they have the same probability for the measurement results,
but their post-measurement states are different. This might be a defect
of representing a measurement process as an observable. As $\mathbf{O}_{1}=\mathbf{J}_{z}^{2}$,
there is no observable corresponding to the measurement process~${\cal O}_{1}$.}
